Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-27 Draft/Draft.Rmd
Table S1 and figure S1 (list of studies and plant functional groups). Starting also with methods...

---
title: "Plant-pollintor networks worldwide are composed by the same specific building blocks"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here we have compiled 60 networks from 29 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.

@@

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes. Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies. [Explain what macro-descriptors have found i.e. Bascompte, and what pairwise interactions descriptors have accomplished i.e. trait-matching. End explaining Benno simmons work]

@@

We have compiled 60 plant-pollinator networks from 29 different studies [...]

@@

1) over and under represented motifs
```{r}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
str(d)
head(d)

@@

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
#NICE! Can we put motifs in Y axes, and % in X?
```
2) FG-position associations.
```{r}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

>>>>

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
---

@@

Ecological processes leave distinct structural imprints on indirect interactions in mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.

@@

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). However, condensing to species level and the holistic view of the full network involves missing relevant information for the understanding of ecological processes. Intermediate levels to study plant-pollinator networks (meso-scale) have been little explored but can shed light of ecological processes not captured by the traditional approaches used in plant-pollinator network studies.

[Explain what macro-descriptors have found i.e. Bascompte, and what pairwise interactions descriptors have accomplished i.e. trait-matching. End explaining Benno simmons work]

@@

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1111 pollinator species and 6248 of plant-pollinator interactions counted. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

@@

1) over and under represented motifs
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models/Motifs_frequency_percentile.csv")
d <- add_study_id(d)
str(d)
head(d)

@@

#Fig 1 Should be a dot plot (or forest plot) of the mean +- SE of the 15 motifs.
#NICE! Can we put motifs in Y axes, and % in X?
```
2) FG-position associations.
```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
library(lme4)
library(nlme)
library(tidyverse)
library(stringi)
library(ggpubr)
source("../Scripts/Scripts_Alfonso/add_study_id.R")

@@

##REFERENCES

<div id ="refs"></div>

##SUPPLEMENTARY MATERIAL

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align = "left"}
##############################
#TABLE S1. List of studies
##############################

#Load libraries
library(kableExtra)
library(dplyr)

#Create data.frame with references

#vector with number of netw per study
`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")

#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))

`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")

Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003)

#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
#"USA", "Ecuador")

DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
         "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")

references <- data.frame(`First author`, Year, `Number of networks`,   DOI)

colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")

#Check number of studies
#nrow(references) # 18 studies
#check number of networks
#sum(as.numeric(references$`Number of networks`)) #60

references %>%
  arrange(`First author`)%>%
  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),caption = "Table S1. List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=F,position = c("left"))

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=7, fig.width=13, fig.cap="Figure S1. Plant functional groups composition separated in qualitative and quantitative variables. Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group. Plot B) shows the radar plot of the different quantitative variables standardize on the same scale also coloured with the same patterns of colours as qualitative variables per cluster."}

#CODE TO PLOT FUNCTIONAL GROUPS
#IT CAN BE PLOT WITH MUCH LESS CODE BUT NO TIME FOR CLEANING IT

##########################################
#Visualization of plant functional groups#
##########################################

library(cowplot)
library(ggplot2)
library(tidyr)
library(dplyr)
library(reshape2)
library(data.table)
library(patchwork)

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

d$Clusters <- dat_1$Clusters

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]

##############################################################################################################################
#Prepare table qualitative variables
##############################################################################################################################

##############################################################################################################################
#Breeding system
t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))

#Summary to create table
breeding <- t %>%
  group_by(Clusters,Breeding_system) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

breeding <- breeding[,-3]

breeding <- spread(breeding, Clusters, Percentage)

colnames(breeding)[1] <- "Category"

Trait <- data.frame(Trait= c(rep("Breeding system", 3)))

Breeding_system <- cbind(Trait, breeding)

##############################################################################################################################
#Compatibility
str(t)
t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Unisexual flower"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Unisexual flower"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"

t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Unisexual flower", "Self incompatible", "Partially self compatible", "Self compatible"))
#Summary to create table
comp <- t %>%
  group_by(Clusters,IMPUTED_Compatibility) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

comp <- comp[,-3]

comp <- spread(comp, Clusters, Percentage)
#Replace Na's with zeros
comp[is.na(comp)] <- 0
#Set call name os categories per trait
colnames(comp)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Compatibility system", 4)))
#Add column
Compatibility_system <- cbind(Trait, comp)
#Bind rows
bind_rows(Breeding_system, Compatibility_system)

############################################################################################################################################
#Life form
t$life_form <- as.character(t$life_form)
t$life_form[t$life_form =="vine"] <- "Shrub"
t$life_form[t$life_form =="tree"] <- "Tree"
t$life_form[t$life_form =="herb"] <- "Herb"
t$life_form[t$life_form =="shrub"] <- "Shrub"
#Order levels
t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
#Summary to create table
life_form <- t %>%
  group_by(Clusters,life_form) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_form <- life_form[,-3]
#convert to wide
life_form <- spread(life_form, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_form)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life form", 3)))
#Add column
Life_form<- cbind(Trait, life_form)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form)

############################################################################################################################################
t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
#Summary to create table
life_span <- t %>%
  group_by(Clusters,lifespan) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_span <- life_span[,-3]
#convert to wide
life_span <- spread(life_span, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_span)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life span", 2)))
#Add column
Life_span<- cbind(Trait, life_span)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)

############################################################################################################################################
t$Flower_morphology <- as.character(t$Flower_morphology)
t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"

Flower_morphology <- t %>%
  group_by(Clusters,Flower_morphology) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_morphology <- Flower_morphology[,-3]
#convert to wide
Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_morphology)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
#Add column
Flower_morphology<- cbind(Trait, Flower_morphology)
#Replace Na's with zeros
Flower_morphology[is.na(Flower_morphology)] <- 0
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)

############################################################################################################################################
t$Flower_symmetry <- as.character(t$Flower_symmetry)
t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"

Flower_symmetry <- t %>%
  group_by(Clusters,Flower_symmetry) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
Flower_symmetry <- Flower_symmetry[,-3]
#convert to wide
Flower_symmetry <- spread(Flower_symmetry, Clusters, Percentage)
#Set call name os categories per trait
colnames(Flower_symmetry)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Flower symmetry", 2)))
#Add column
Flower_symmetry<- cbind(Trait, Flower_symmetry)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology,Flower_symmetry)
############################################################################################################################################
t$Autonomous_selfing_level <- as.character(t$Autonomous_selfing_level)
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="none"] <- "None"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="low"] <- "Low"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="medium"] <- "Medium"
t$Autonomous_selfing_level[t$Autonomous_selfing_level =="high"] <- "High"

#Order levels
t$Autonomous_selfing_level <- factor(t$Autonomous_selfing_level, levels=c("High", "Medium", "Low", "None"))

Selfing <- t %>%
  group_by(Clusters,Autonomous_selfing_level) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Selfing <- Selfing[,-3]
#convert to wide
Selfing <- spread(Selfing, Clusters, Percentage)
#Set call name os categories per trait
colnames(Selfing)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Selfing level", 2)))
#Replace Na's with zeros
Selfing[is.na(Selfing)] <- 0
#Add column
Selfing_1 <- cbind(Trait, Selfing)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Selfing_1)

############################################################################################################################################
t$Nectar_presence_absence <- as.character(t$Nectar_presence_absence)
t$Nectar_presence_absence[t$Nectar_presence_absence =="yes"] <- "Yes"
t$Nectar_presence_absence[t$Nectar_presence_absence =="no"] <- "No"

Nectar <- t %>%
  group_by(Clusters,Nectar_presence_absence) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

#delete column to convert to wide
Nectar <- Nectar[,-3]
#convert to wide
Nectar <- spread(Nectar, Clusters, Percentage)
#Set call name os categories per trait
colnames(Nectar)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Nectar", 2)))
#Replace Na's with zeros
Nectar[is.na(Nectar)] <- 0
#Add column
Nectar <- cbind(Trait, Nectar)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar)

##############################################################################################################################
#Prepare table quantitative variables
##############################################################################################################################

Selfing <-  t %>% group_by(Clusters)%>% 
  select(Autonomous_selfing_level_fruit_set) %>% # select variables to summarise
  summarise_each(funs(min = min,
                     # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                    sd = sd))

s1 <- as.data.frame(t(Selfing))
#set colnames
colnames(s1) <- c("1","2","3","4","5")
#remove the cluster row
s1 <- s1[-1,]
#convert rownames to 1st columns
s1 <- setDT(s1, keep.rownames = "TRUE")[]
colnames(s1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Autonomous selfing", 5)))
#Add column
Selfing <- cbind(Trait, s1)

##############################################################################################################################
flower_number <-  t %>% group_by(Clusters)%>% 
  select(Flowers_per_plant) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f1 <- as.data.frame(t(flower_number))
#set colnames
colnames(f1) <- c("1","2","3","4","5")
#remove the cluster row
f1 <- f1[-1,]
#convert rownames to 1st columns
f1 <- setDT(f1, keep.rownames = "TRUE")[]
colnames(f1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower number", 5)))
#Add column
Flower_number <- cbind(Trait, f1)

##############################################################################################################################
Flowers_per_inflorescence <-  t %>% group_by(Clusters)%>% 
  select(Flowers_per_inflorescence) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f_i_1 <- as.data.frame(t(Flowers_per_inflorescence))
#set colnames
colnames(f_i_1) <- c("1","2","3","4","5")
#remove the cluster row
f_i_1 <- f_i_1[-1,]
#convert rownames to 1st columns
f_i_1 <- setDT(f_i_1, keep.rownames = "TRUE")[]
colnames(f_i_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flowers per inflorescence", 5)))
#Add column
Flower_per_inflo <- cbind(Trait, f_i_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo)

##############################################################################################################################
Floral_unit_width <-  t %>% group_by(Clusters)%>% 
  select(Floral_unit_width) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

f_u_w_1 <- as.data.frame(t(Floral_unit_width))
#set colnames
colnames(f_u_w_1) <- c("1","2","3","4","5")
#remove the cluster row
f_u_w_1 <- f_u_w_1[-1,]
#convert rownames to 1st columns
f_u_w_1 <- setDT(f_u_w_1, keep.rownames = "TRUE")[]
colnames(f_u_w_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Inflorescence width", 5)))
#Add column
Inflo_width <- cbind(Trait, f_u_w_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width)

##############################################################################################################################
Corolla_diameter_mean <-  t %>% group_by(Clusters)%>% 
  select(Corolla_diameter_mean) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

c_w_1 <- as.data.frame(t(Corolla_diameter_mean))
#set colnames
colnames(c_w_1) <- c("1","2","3","4","5")
#remove the cluster row
c_w_1 <- c_w_1[-1,]
#convert rownames to 1st columns
c_w_1 <- setDT(c_w_1, keep.rownames = "TRUE")[]
colnames(c_w_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower width", 5)))
#Add column
Flower_width <- cbind(Trait, c_w_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width)

##############################################################################################################################
Corolla_length_mean <-  t %>% group_by(Clusters)%>% 
  select(Corolla_length_mean) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

c_l_1 <- as.data.frame(t(Corolla_length_mean))
#set colnames
colnames(c_l_1) <- c("1","2","3","4","5")
#remove the cluster row
c_l_1 <- c_l_1[-1,]
#convert rownames to 1st columns
c_l_1 <- setDT(c_l_1, keep.rownames = "TRUE")[]
colnames(c_l_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Flower length", 5)))
#Add column
Flower_length<- cbind(Trait, c_l_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length)

##############################################################################################################################
STYLE_IMPUTED <-  t %>% group_by(Clusters)%>% 
  select(STYLE_IMPUTED) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

s_l_1 <- as.data.frame(t(STYLE_IMPUTED))
#set colnames
colnames(s_l_1) <- c("1","2","3","4","5")
#remove the cluster row
s_l_1 <- s_l_1[-1,]
#convert rownames to 1st columns
s_l_1 <- setDT(s_l_1, keep.rownames = "TRUE")[]
colnames(s_l_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Style length", 5)))
#Add column
Style_length<- cbind(Trait, s_l_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length)

##############################################################################################################################

OVULES_IMPUTED <-  t %>% group_by(Clusters)%>% 
  select(OVULES_IMPUTED) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

o_n_1 <- as.data.frame(t(OVULES_IMPUTED))
#set colnames
colnames(o_n_1) <- c("1","2","3","4","5")
#remove the cluster row
o_n_1 <- o_n_1[-1,]
#convert rownames to 1st columns
o_n_1 <- setDT(o_n_1, keep.rownames = "TRUE")[]
colnames(o_n_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Ovule number", 5)))
#Add column
Ovule_number <- cbind(Trait, o_n_1)

bind_rows(Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Ovule_number)

##############################################################################################################################

IMPUTED_plant_height_mean_m <-  t %>% group_by(Clusters)%>% 
  select(IMPUTED_plant_height_mean_m) %>% # select variables to summarise
  summarise_each(funs(min = min,
                      # q25 = quantile(., 0.25), 
                      median = median, 
                      #q75 = quantile(., 0.75), 
                      max = max,
                      mean = mean, 
                      sd = sd))

p_h_1 <- as.data.frame(t(IMPUTED_plant_height_mean_m))
#set colnames
colnames(p_h_1) <- c("1","2","3","4","5")
#remove the cluster row
p_h_1 <- p_h_1[-1,]
#convert rownames to 1st columns
p_h_1 <- setDT(p_h_1, keep.rownames = "TRUE")[]
colnames(p_h_1)[1] <- "Category"
#Create data frame to add grouping variable
Trait <- data.frame(Trait= c(rep("Plant height", 5)))
#Add column
Plant_height <- cbind(Trait, p_h_1)

#Bind quantitative and qualitative variables
Table_all_traits <- bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology, Flower_symmetry,Selfing_1, Nectar,
          Selfing, Flower_number, Flower_per_inflo, Inflo_width, Flower_width, Flower_length, Style_length, Ovule_number, Plant_height)

#Select just two decimals
is.num <- sapply(Table_all_traits, is.numeric)
Table_all_traits[is.num] <- lapply(Table_all_traits[is.num], round, 2)

colnames(Table_all_traits) <- c("Trait", "Category", "Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4", "Cluster 5")

#LOAD LIBRARIES
#devtools::install_github("ricardo-bion/ggradar", dependencies=TRUE)
suppressPackageStartupMessages(library(dplyr))
library(scales)
library(tibble)
library(ggradar)
library(janitor)
library(grid)
library(dplyr)
library(lubridate)
#QUANTITATIVVE VARIABLES

#generate subset of quantitative variables for plotting
quant_median <- subset(Table_all_traits, Category=="median")

#delete col number 2
quant_median <- quant_median[,-2]

#transpose dataframe
final_df <- as.data.frame(t(quant_median))

#rownames to colnames (1st one)
final_df_1 <- final_df %>% row_to_names(row_number = 1)

#Convert all variables to numeric
final_df_2 <- sapply(final_df_1, function(x) as.numeric(as.character(x)))

#set back the missed rownames in the processing
rownames(final_df_2) <- rownames(final_df_1)

# Convert to dataframe
final_df_2 <- as.data.frame(final_df_2)

# Scale values and set rowname as column
final_df_3 <-final_df_2 %>% rownames_to_column( var = "group" ) %>%   mutate_at(vars(-group),funs(rescale))

#Plot Radar
#ggradar(final_df_3)

#QUALITATIVE VARIABLES

#LOAD DATA
#read unscaled trait data in order to visualize better the clusters
d <- read.csv("../Data/Csv/all_species_imputed_trait_data_forest_data.csv")

dat_1 <- read.csv("../Data/Csv/imputed_trait_data_hclust_5_clusters_forest_data.csv", row.names = "X")

d$Clusters <- dat_1$Clusters

#select columns of interest
t <- d[c("Breeding_system","IMPUTED_Compatibility","Autonomous_selfing_level",
         "Autonomous_selfing_level_fruit_set", "Flower_morphology", "Flower_symmetry", "Flowers_per_plant", "Flowers_per_inflorescence",
         "Floral_unit_width", "Corolla_diameter_mean", "Corolla_length_mean", "STYLE_IMPUTED", "OVULES_IMPUTED", "life_form", "lifespan",
         "IMPUTED_plant_height_mean_m", "Nectar_presence_absence", "Clusters")]

##############################################################################################################################
#Prepare table qualitative variables
##############################################################################################################################

##############################################################################################################################
#Breeding system
t$Breeding_system <- factor(t$Breeding_system, levels=c("Dioecious", "Monoecious", "Hermaphrodite"))

#Summary to create table
breeding <- t %>%
  group_by(Clusters,Breeding_system) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

breeding <- breeding[,-3]

breeding <- spread(breeding, Clusters, Percentage)

colnames(breeding)[1] <- "Category"

Trait <- data.frame(Trait= c(rep("Breeding system", 3)))

Breeding_system <- cbind(Trait, breeding)

##############################################################################################################################
#Compatibility
str(t)
t$IMPUTED_Compatibility <- as.character(t$IMPUTED_Compatibility)
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="dioecious"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="monoecious"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_incompatible"] <- "Self incompatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="partially_self_compatible"] <- "Partially self compatible"
t$IMPUTED_Compatibility[t$IMPUTED_Compatibility=="self_compatible"] <- "Self compatible"

t$IMPUTED_Compatibility <- factor(t$IMPUTED_Compatibility, levels=c("Self incompatible", "Partially self compatible", "Self compatible"))
#Summary to create table
comp <- t %>%
  group_by(Clusters,IMPUTED_Compatibility) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)

comp <- comp[,-3]

comp <- spread(comp, Clusters, Percentage)
#Replace Na's with zeros
comp[is.na(comp)] <- 0
#Set call name os categories per trait
colnames(comp)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Compatibility system", 3)))
#Add column
Compatibility_system <- cbind(Trait, comp)
#Bind rows
bind_rows(Breeding_system, Compatibility_system)

############################################################################################################################################
#Life form
t$life_form <- as.character(t$life_form)
t$life_form[t$life_form =="vine"] <- "Shrub"
t$life_form[t$life_form =="tree"] <- "Tree"
t$life_form[t$life_form =="herb"] <- "Herb"
t$life_form[t$life_form =="shrub"] <- "Shrub"
#Order levels
t$life_form <- factor(t$life_form, levels=c("Tree", "Shrub", "Herb"))
#Summary to create table
life_form <- t %>%
  group_by(Clusters,life_form) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_form <- life_form[,-3]
#convert to wide
life_form <- spread(life_form, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_form)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life form", 3)))
#Add column
Life_form<- cbind(Trait, life_form)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form)

############################################################################################################################################
t$lifespan <- factor(t$lifespan, levels=c("Perennial","Short lived"))
#Summary to create table
life_span <- t %>%
  group_by(Clusters,lifespan) %>%
  summarise (n = n()) %>%
  mutate(Percentage = n / sum(n)*100)
#delete column to convert to wide
life_span <- life_span[,-3]
#convert to wide
life_span <- spread(life_span, Clusters, Percentage)
#Set call name os categories per trait
colnames(life_span)[1] <- "Category"
#Create new column
Trait <- data.frame(Trait= c(rep("Life span", 2)))
#Add column
Life_span<- cbind(Trait, life_span)
#Bind rows
bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span)

############################################################################################################################################
#t$Flower_morphology <- as.character(t$Flower_morphology)
#t$Flower_morphology[t$Flower_morphology=="Funnelform"] <- "Campanulate"
#t$Flower_morphology[t$Flower_morphology=="Spike"] <- "Brush"
#
#Flower_morphology <- t %>%
#  group_by(Clusters,Flower_morphology) %>%
#  summarise (n = n()) %>%
#  mutate(Percentage = n / sum(n)*100)
##delete column to convert to wide
#Flower_morphology <- Flower_morphology[,-3]
##convert to wide
#Flower_morphology <- spread(Flower_morphology, Clusters, Percentage)
##Set call name os categories per trait
#colnames(Flower_morphology)[1] <- "Category"
##Create new column
#Trait <- data.frame(Trait= c(rep("Flower shape", 6)))
##Add column
#Flower_morphology<- cbind(Trait, Flower_morphology)
##Replace Na's with zeros
#Flower_morphology[is.na(Flower_morphology)] <- 0
##Bind rows
#bind_rows(Breeding_system, Compatibility_system, Life_form, Life_span,Flower_morphology)
#
############################################################################################################################################
t$Flower_symmetry <- as.character(t$Flower_symmetry)
t$Flower_symmetry[t$Flower_symmetry =="actinomorphic"] <- "Actinomorphic"
t$Flower_symmetry[t$Flower_symmetry =="zygomorphic"] <- "Zygomorphic"
